createData_linear_modeling

### 2016-06-16 portfolio/analysis/4a-createData_linear_modeling.Rmd
Clean up data creation script
Note that since we have different raw data
a couple of these things might not work

## Load cleaned data  
```{r dataLoad, warning = FALSE, message=FALSE, results="hide", echo=FALSE}
library(dplyr)
library(knitr)
library(mgcv)
library(ggplot2)
library(randomForest)
library(MASS)
library(zoo)
library(MatchIt)
library(metafolio)
library(randomForest)
library(date)

#load("cfecCleaned2.Rdata")
cfec <- feather::read_feather("data/cfec.feather")

@@

# remove white space in 2nd position
idx = which(substr(cfec$p_fshy, 2, 2) == " ")
cfec$p_fshy[idx] = paste(substr(cfec$p_fshy[idx], 1, 1), 
  substr(cfec$p_fshy[idx], 3, length(cfec$p_fshy[idx])), sep="")

region<-read.csv("areas/regions.csv")
region<-region[,c(1:2)] #don’t include “assigned by” column
cfec<-left_join(cfec,region)
#cfec$region <- replace(cfec$region, is.na(cfec$region), "Unassigned")
```

@@

```{r, echo=FALSE}
deflationTable = data.frame(year = 1985:2014, defl = c(0.57236, 0.58393, 0.59879, 0.61974,  
0.64388, 0.66774, 0.68993, 0.70564, 0.72244, 0.73781,  
0.75321, 0.76695, 0.78009, 0.78855, 0.80061,  
0.81883, 0.83753, 0.85038, 0.86729, 0.89114,  
0.91981, 0.94812, 0.97334, 0.9925, 1,  
1.01217, 1.03307, 1.05213, 1.06926, 1.08682))

# Adjust price and g_earn for inflation
cfec$year = as.numeric(cfec$year)
cfec$day = substr(cfec$landdate, 6, 10)
cfec$g_price = cfec$g_price/deflationTable$defl[cfec$year-1984]
cfec$g_earn = cfec$g_earn/deflationTable$defl[cfec$year-1984]
```

### Function definiton  
We need to define a few functions for calculating diversity. We'll use the Simpson's diversity index (HHI) to calculate the entropy-based inverse, which is a proxy for effective species diversity. Note the C++ version is commented out below,

@@

simp.div = function(x) {
  1/sum((x/sum(x))^2)
}

#library(Rcpp)
#cppFunction('double simpCpp(NumericVector x) {
#  double y = 1/sum((x/sum(x))^2);
#  return y;
#}')

@@

```{r}
cfecnew = cfec
cfec.1boat = group_by(cfecnew, p_holder, year) %>% 
  summarize(nBoat = length(unique(cadfg))) %>%
  filter(nBoat==1) %>% 
  left_join(cfecnew)

# Deal with setnet fisheries, where lots of p_holder
# share same codes
cfec.1boat = group_by(cfec.1boat, cadfg, year) %>% 
  summarize(nPerson = length(unique(p_holder))) %>%
  filter((nPerson==1 & cadfg %in% c(27960,27961) == FALSE) | cadfg %in% c(27960,27961)) %>% 
  left_join(cfec.1boat)

@@

cfecAnnual = group_by(cfecnew, p_holder, year) %>%
  summarize(permit = p_fshy[1], boat = cadfg2[1], 
    days = diff(range(day) + 1), 
    ngear = length(unique(gearn)),
    nspec = length(unique(specn)),
    npermit = length(unique(p_fshy)),
    revenue = sum(g_earn),
    length = mean(VLength, na.rm=T))

cfecAnnual = group_by(cfecAnnual, p_holder, year) %>%
  filter(npermit == 1)

@@

saveRDS(cfecAnnual.salmon, file="salmon_linearModeling_complete.rds")
saveRDS(cfecAnnual.nonsalmon, file="nonsalmon_linearModeling_complete.rds")

>>>>

## Load cleaned data  
```{r dataLoad, warning = FALSE, message=FALSE, results="hide", echo=FALSE}
library(dplyr)
library(knitr)
# library(mgcv)
library(ggplot2)
# library(randomForest)
# library(MASS)
# library(zoo)
# library(MatchIt)
# library(metafolio)
# library(randomForest)
library(date)

devtools::load_all("../../pfxr/")

#load("cfecCleaned2.Rdata")
cfec <- feather::read_feather("../data-generated/cfec.feather")

@@

# remove white space in 2nd position
idx = which(substr(cfec$p_fshy, 2, 2) == " ")
cfec$p_fshy[idx] = paste(substr(cfec$p_fshy[idx], 1, 1), 
  substr(cfec$p_fshy[idx], 3, length(cfec$p_fshy[idx])), sep="")
```

@@

### Function definition  
We need to define a few functions for calculating diversity. We'll use the Simpson's diversity index (HHI) to calculate the entropy-based inverse, which is a proxy for effective species diversity. Note the C++ version is commented out below,

@@

@@

```{r}
cfecnew = cfec
cfec.1boat = group_by(cfecnew, p_holder, year) %>% 
  mutate(nBoat = length(unique(cadfg))) %>%
  filter(nBoat==1)

# Deal with setnet fisheries, where lots of p_holder
# share same codes
cfec.1boat = group_by(cfec.1boat, cadfg, year) %>% 
  mutate(nPerson = length(unique(p_holder))) %>%
  filter((nPerson==1 & cadfg %in% c(27960,27961) == FALSE) | cadfg %in% c(27960,27961))

@@

cfecAnnual = group_by(cfecnew, p_holder, year) %>%
  summarize(permit = p_fshy[1], boat = cadfg[1], # TODO cadfg2?
    days = diff(range(day) + 1), 
    ngear = length(unique(gearn)),
    nspec = length(unique(specn)),
    npermit = length(unique(p_fshy)),
    revenue = sum(g_earn),
    length = mean(vlength, na.rm=T))

cfecAnnual = filter(cfecAnnual, npermit == 1)

@@

saveRDS(cfecAnnual.salmon, file="../data-generated/salmon_linearModeling_complete.rds")
saveRDS(cfecAnnual.nonsalmon, file="../data-generated/nonsalmon_linearModeling_complete.rds")
